\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2014-11-25 tex/supplement.tex
move figures into main text and switch bibliography format

Suppose that our Jacobian $A$ is an $n \times n$ matrix with real coefficients, connectivity $\connectivity$, and denote the proposition ``$A$ is stable'' as $\mathrm{stab}(A)$.  Then we may compute the robustness of this proposition using \ref{eq:robustness} once we have specified the probability densities $\mu$ and $\mu'$.  In general, these will depend upon the parameters of the non-linear system.  For the purpose of the current investigation, we shall make the ansatz that these are such that the distribution of entries of $A$ is (at least approximately) the uniform distribution $\mathcal{U}(-1,1)$ on the $\connectivity$-dimensional hypercube, $H^\connectivity$, of edge length $r=2$, centered about the origin. To model the perturbations, we resample the elements $k_1, k_2, \ldots k_m$ of this matrix from the same uniform distribution yielding
$$
\mu_{k_1,\ldots,k_m}(x,y) = \prod_{y \notin \{x_1, \ldots, x_m\} } \delta(x_j-y_j) \prod_{y \notin \{x_1,\cdots,x_m\}} \mathbf{1}_{[-1,1]} (y_j) \mathbf{1}_{[-1,1]} (x_j)
$$
Under these assumptions, the expression for robustness becomes a special case of \ref{eq:robustness}:
\begin{equation}\label{eq:condprobgen}
 R (\mathrm{stab}, \mu'_{k_1, \ldots, k_m}) =
  \frac{\int_{H^\connectivity} dx_1 \cdots dx_d \int_{H^m} {dx'}_{k_1} \cdots {dx'}_{k_m}\,
    \mathbf{1}_{stab} \mathbf{1}_{stab'}}
  {\int_{H^\connectivity} dx_1 \cdots dx_d  \, \mathbf{1}_{stab}(x_1 \cdots x_d)},
\end{equation}
where we made the abbreviations
\begin{align*}
\mathbf{1}_{stab} &= \mathbf{1}_{stab}(x_1 \cdots x_{k_1} \cdots x_{k_m} \cdots x_\connectivity), \\
\mathbf{1}_{stab'} &= \mathbf{1}_{stab'}(x_1 \cdots {x'}_{k_1} \cdots {x'}_{k_m}  \cdots x_d),
\end{align*}
i.e. $\mathbf{1}_{stab'}$ corresponds to replacing $x_{k_1}, \ldots x_{k_m}$ with their primed counterparts.

While one can resample a fixed subset of the links, more typically we will be randomly selecting which links to resample with a uniform distribution on the links.  The result of this operation corresponds to averaging our quantity over subsets of links:
\begin{equation}\label{eq:robavgoverlinks}
\langle R (\hbox{stab}, \mu') \rangle_m =
\frac{1}{\binom{\connectivity}{m}}
\sum_{\{k_1, k_2, \ldots k_m\} \subset \{1, 2,, \ldots \connectivity\}}
R (\hbox{stab}, \mu'_{k_1, \ldots, k_m})
\end{equation}
We are fundamentally interested in the relationship between \ref{eq:condprobgen} and \ref{eq:robavgoverlinks} and topological properties of systems that derive from their associated graphs. In order to investigate this further, we must characterize properties of system graphs in order to evaluate correlations of those properties with dynamical robustness.

@@

@@

\subsection{Stability and robustness analysis of particular system ensembles}
For systems having two variables, we can analytically compute the probability of stability and robustness from \ref{eq:condprobgen}. For those having three variables, we can estimate these same quantities using Monte Carlo simulations. Systems of larger size can be analyzed using the symmetry properties of robustness extracted from this analysis. For two-variable systems having $2 \times 2$ Jacobian matrices, the aforementioned stability criteria result in the conditions $T < 0$ and $D >
0$ where $T$ and $D$ denote the trace and the determinant. Suppose we have a stable matrix
$$
\begin{bmatrix}
a & b \\
d & c
\end{bmatrix}
$$
where $a + c < 0$ and $ac > bd$.  For the case in which $x_1=a,\,x_2=b,\,x_3=c,\,x_4=d$ we need to compute what corresponds to $R(\mathrm{stab},\mu'_k)$ where $k=1 \ldots 4$. By symmetry, there are two cases to consider; resampling $a$ is equivalent to resampling $c$ and resampling $b$ is equivalent to resampling $d$ so we only need to explicitly compute $ R(\mathrm{stab},\mu'_1)$ and $R(\mathrm{stab},\mu'_2)$. Suppose that we resample $b$ to compute $R(\mathrm{stab},\mu'_2)$.
% \begin{strip}
% \begin{align}\label{eq:condprob}
% P\left(\begin{pmatrix}
% a & b' \\
% d & c
% \end{pmatrix} \textrm{stable } \bigg| \begin{pmatrix}
% a & b \\
% d & c
% \end{pmatrix} \textrm{stable } \right)
% & = \frac{P\left(\begin{pmatrix}
% a & b \\
% d & c
% \end{pmatrix} \textrm{stable and } \begin{pmatrix}
% a & b' \\
% d & c
% \end{pmatrix} \textrm{stable } \right)}{P\left(\begin{pmatrix}
% a & b \\
% d & c
% \end{pmatrix} \textrm{stable } \right)}.
% \end{align}
The denominator of \ref{eq:condprobgen} in this case is given by
\begin{align*}
P\left(\textrm{stab } \left( \begin{bmatrix}
a & b \\
d & c
\end{bmatrix} \right) \right) = \frac{\int_{\genfrac{}{}{0pt}{}{\genfrac{}{}{0pt}{}{ac>bd}{a+c<0}}{H^4}} da\,db\,dc\,dd\,1}{\int_{H^4} da\,db\,dc\,dd\,1}.
\end{align*}
Since the trace does not involve $b$, the $T<0$ condition will be satisfied automatically and we only need to examine the determinant. Thus, we have the inequalities $ac > b'd$ and $-1 < b' < 1$ in addition to the previous constraints leading to an expression for the numerator of \ref{eq:condprobgen}
\begin{align*}
P\left(\textrm{stab} \left( \begin{bmatrix}
a & b \\
d & c
\end{bmatrix} \right) \textrm{ and stab} \left( \begin{bmatrix}
a & b' \\
d & c
\end{bmatrix} \right) \right) = \frac{\int_{{{ac>b'd \atop ac>bd} \atop a+c<0} \atop H^5} da\,db\,dc\,dd\,db'\,1}{\int_{H^5} da\,db\,dc\,dd\,db'\,1}.
\end{align*}
The analogous equation for resampling $a$ is
\begin{align*}
P\left(\textrm{stab} \left( \begin{bmatrix}
a & b \\
d & c
\end{bmatrix} \right) \textrm{ and stab} \left( \begin{bmatrix}
a' & b \\
d & c
\end{bmatrix} \right) \right) = \frac{\int_{{{{a'c>bd \atop a' + c < 0} \atop ac>bd} \atop a+c<0} \atop H^5} da\,db\,dc\,dd\,da'\,1}{\int_{H^5} da\,db\,dc\,dd\,da'\,1}.
\end{align*}
Using this approach the probability of stability and of robustness for all two variable systems is given in \ref{tab:structstabmat}.

The analogous results for all three variable systems are computed using Monte Carlo integration and shown in \ref{tab:structstabmat3} and \reffigrobustconnect. This process is associated with some error relative to the exact integration described above. If we sample $N = N_{\mathrm{stab}} + N_{\mathrm{unstab}}$ matrices where each has some probability $\theta$ of being stable then $N_{\mathrm{stab}}$ has a binomial distribution. We can compute a sample estimate for $\theta$, $\hat{\theta} = \frac{N_{\mathrm{stab}}}{N}$ \cite{Murphy2012}. The posterior distribution in this case is known to be a Beta distribution as a result of Beta-Binomial conjugacy
$$
\mathrm{Beta}(\theta | \mathcal{D}) = \mathrm{Beta}(\theta | N_{\mathrm{stab}} + a, N_{\mathrm{unstab}} + b)
$$
where $a$ and $b$ are the hyperparameters of the Beta prior and we consider the uninformative uniform prior corresponding to $a=b=1$. We consider the maximum a posteriori estimate
$$\hat{\theta}_{MAP} = \frac{a + N_{\mathrm{stab}} - 1}{a + b + N - 2}$$
which corresponds in this case to the maximum likelihood estimate
$$
\hat{\theta}_{MLE} = \frac{N_{\mathrm{stab}}}{N}.
$$
This estimate is characterized by the variance of the posterior Beta distribution
$$
\mathrm{var}(\theta | \mathcal{D}) = \frac{(a+N_{\mathrm{stab}})(b+N_{\mathrm{unstab}})}{(a + N_{\mathrm{stab}} + b + N_{\mathrm{unstab}})^2(a + N_{\mathrm{stab}} + b + N_{\mathrm{unstab}}+1)}
$$
Since for the chosen prior $a=b=1 \ll N$ this simplifies to
$$
\mathrm{var}(\theta | \mathcal{D}) = \frac{\hat{\theta}(1-\hat{\theta})}{N}
$$
yielding the error estimate given by the associated standard deviation. In all simulations we use $N~=~10000$ so that the maximum error for $\hat{\theta}~=~0.5$ is $\sigma~=~\sqrt{\mathrm{var}(\theta | \mathcal{D})} \approx 0.005$.

@@

@@

Using these observations, we may express the robustness of a graph in
terms of the robustnesses of its strongly connected components.  If
each component $C_i$ of our graph $G$ has $v_i$ vertices, connectivity
$\connectivity_i$, and there are $\ell_{ij}$ links between components
$i$ and $j$, then there are a total of
$\sum_{i,j \in \hier(G)} \ell_{ij} + \sum_{i=1}^n \connectivity_i$
links in $G$.  If we resample a randomly chosen link in a component
$C_i$, then the probability that the system will remain stable after
resampling is $\langle R(\hbox{stab} (C_i), \mu') \rangle_1$.  If we resample a link
between components $C_i$ and $C_j$, the system will remain stable with
probability 1.  Hence, the probability that the system will remain
stable upon resampling a random link is the weighted average of these
probabilities:
\begin{align}\label{eq:sccrobustness}
\langle R(\hbox{stab} (G), \mu') \rangle_1 =
\frac{\sum\limits_{(i,j) \in \hier(G)} \ell_{ij} +
      \sum\limits_{i=1}^n \connectivity_i \langle R(\textrm{stab}(C_i),\mu') \rangle_1}
     {\sum\limits_{(i,j) \in \hier(G)} \ell_{ij} +
      \sum\limits_{i=1}^n \connectivity_i}.
\end{align}
For instance, if our graph is the one in \reffigscc (middle panels), then we have two connected components, one with two nodes, and one with one node.  From \ref{tab:structstabmat}, we know that the graph with two nodes has probability $0.25$ of being stable and robustness $0.62$.  The graph with one node corresponds to a $1 \times 1$ matrix, so we have probability $0.5$ of stability and robustness $0.5$.  Thus, the probability of our 3-node graph being stable is $0.5 \times 0.25 = 0.125$ and its robustness is
\[
\langle R(\textrm{stab}(G),\mu') \rangle_1 = \frac{2 + 0.5 + 4 \times 0.62}{2 + 1 + 4} = 0.714,
\]
which agrees with the value computed in \ref{tab:structstabmat} up to
sampling error.

@@

Since every acyclic digraph can be embedded into a totally ordered
set, we may assume without loss of generality that our components have
been ordered in a way such that, if $(i,j) \in \hier(G)$, then $i <
j$.  Hence, after substituting into our expression and simplifying
using the identity
$$\sum_{i=1}^{n-1}\sum_{j=i+1}^{n}v_i
v_j~=~\frac{1}{2} \left( \sum_{i=1}^{n} v_i \right)^2-\frac{1}{2} \sum_{i=1}^{n}
v_i^2,$$
we arrive at the following upper bound on robustness in terms
of the connected components:
\begin{align} \label{eq:sccmaxrobustness}
R_{\mathrm{max}}(C_1, \ldots C_n) =
\frac{\frac{1}{2} ((\sum_{i=1}^n v_i)^2 - \sum_{i=1}^n v_i^2) +
                    \sum_{i=1}^n \connectivity_i \langle R(\hbox{stab}(C_i),\mu') \rangle_1}
     {\frac{1}{2} ((\sum_{i=1}^n v_i)^2 - \sum_{i=1}^n v_i^2) +
                    \sum_{i=1}^n \connectivity_i}.
\end{align}
Furthermore, this bound is attained.  Suppose that $G_{\mathrm{tot}}$
is the graph on $n$ nodes with a link from node $i$ to node $j$
whenever $i < j$.  Then, by the construction described in the previous
section on network hierachy, we have a graph $G_{\mathrm{max}}$ such
that the components of $G_{\mathrm{max}}$ are $C_1, \ldots C_n$ and
$\hier (G_{\mathrm{max}}) = G_{\mathrm{tot}}$.  By our formula,
$\langle R(\hbox{stab} (G_{\mathrm{max}}), \mu') \rangle_1 = R_{\mathrm{max}}(C_1, \ldots C_n)$.

This argument also works when we resample more than one entry,
although the notation becomes more complicated.  Suppose that we
resample $m$ nodes.  Define
\begin{equation*}
M = \left\{(m_0, m_1, \ldots, m_n) \,\bigg|\,
m = \sum_{i=0}^n m_i \quad\&\quad
m_0 \le \sum_{i=1}^{n-1} \sum_{j=i+1}^n \ell_{ij} \quad\&\quad
(\forall i \in \{1, \ldots, n\}) \; m_i < \connectivity_i \right\}.
\end{equation*}
Then, given $(m_0, m_1, \ldots, m_n) \in M$, there are ${m \choose
m_0, m_1, \ldots. m_n}$ ways of choosing $m_i$ links from $C_i$ and
$m_0$ links between strongly connected components.  Hence, our
weighted average becomes
\begin{equation}
\langle R(\hbox{stab} (G), \mu') \rangle_m =
\frac{\sum\limits_{(m_0, m_1, \ldots m_n) \in M}
      {m \choose m_0, m_1, \ldots. m_n}
      \left(m_0 + \sum\limits_{i=1}^n m_i \langle R(\hbox{stab} (C_i), \mu') \rangle_{m_i} \right)}
     {\sum\limits_{(m_0, m_1, \ldots m_n) \in M}
      {m \choose m_0, m_1, \ldots. m_n} m}
\end{equation}

>>>>

Suppose that our Jacobian $A$ is an $n \times n$ matrix with real coefficients, connectivity $\connectivity$, and denote the proposition ``$A$ is stable'' as $\mathrm{stab}(A)$.  Then we may compute the robustness of this proposition using \ref{eq:robustness} once we have specified the probability densities $\mu$ and $\mu'$.  In general, these will depend upon the parameters of the non-linear system.  For the purpose of the current investigation, we shall make the ansatz that these are such that the distribution of entries of $A$ is (at least approximately) the uniform distribution $\mathcal{U}(-1,1)$ on the $\connectivity$-dimensional hypercube, $H^\connectivity$, of edge length $r=2$, centered about the origin. To model the perturbations, we resample the elements $k_1, k_2, \ldots k_m$ of this matrix from the same uniform distribution yielding
\begin{widetext}
$$
\mu_{k_1,\ldots,k_m}(x,y) = \prod_{y \notin \{x_1, \ldots, x_m\} } \delta(x_j-y_j) \prod_{y \notin \{x_1,\cdots,x_m\}} \mathbf{1}_{[-1,1]} (y_j) \mathbf{1}_{[-1,1]} (x_j)
$$
\end{widetext}
Under these assumptions, the expression for robustness becomes a special case of \ref{eq:robustness}:
\begin{widetext}
\begin{equation}\label{eq:condprobgen}
 R (\mathrm{stab}, \mu'_{k_1, \ldots, k_m}) =
  \frac{\int_{H^\connectivity} dx_1 \cdots dx_d \int_{H^m} {dx'}_{k_1} \cdots {dx'}_{k_m}\,
    \mathbf{1}_{stab} \mathbf{1}_{stab'}}
  {\int_{H^\connectivity} dx_1 \cdots dx_d  \, \mathbf{1}_{stab}(x_1 \cdots x_d)},
\end{equation}
\end{widetext}
where we made the abbreviations
\begin{align*}
\mathbf{1}_{stab} &= \mathbf{1}_{stab}(x_1 \cdots x_{k_1} \cdots x_{k_m} \cdots x_\connectivity), \\
\mathbf{1}_{stab'} &= \mathbf{1}_{stab'}(x_1 \cdots {x'}_{k_1} \cdots {x'}_{k_m}  \cdots x_d),
\end{align*}
i.e. $\mathbf{1}_{stab'}$ corresponds to replacing $x_{k_1}, \ldots x_{k_m}$ with their primed counterparts.

While one can resample a fixed subset of the links, more typically we will be randomly selecting which links to resample with a uniform distribution on the links.  The result of this operation corresponds to averaging our quantity over subsets of links:
\begin{widetext}
\begin{equation}\label{eq:robavgoverlinks}
\langle R (\hbox{stab}, \mu') \rangle_m =
\frac{1}{\binom{\connectivity}{m}}
\sum_{\{k_1, k_2, \ldots k_m\} \subset \{1, 2,, \ldots \connectivity\}}
R (\hbox{stab}, \mu'_{k_1, \ldots, k_m})
\end{equation}
\end{widetext}
We are fundamentally interested in the relationship between \ref{eq:condprobgen} and \ref{eq:robavgoverlinks} and topological properties of systems that derive from their associated graphs. In order to investigate this further, we must characterize properties of system graphs in order to evaluate correlations of those properties with dynamical robustness.

@@

\begin{figure*}[!ht]
\centering
\noindent\includegraphics[width=0.8\textwidth]{fig/modsccsym.pdf}
\caption{{\bf Open systems, strongly connected components and symmetries of robustness.} (A) Example of the combination of open system modules to construct closed systems. (B) SCCs highlighted in gray for each of the four graphs representing the interdependencies relevant to four different three variable systems. The most hierarchical network, top panel, is the one that maximizes the number of SCCs and the number of links between them. We therefore define hierarchy as $max(\hbox{ED}) - \hbox{ED}$ where ED is the edit distance representing the number of link addition/deletion operations necessary to transform a given graph into the most hierarchical one. The two panels in the middle represent examples of hierarchical modular systems that posess both modularity (i.e. SCCs with more than one variable) and hierarchy. (C) Symmetries of the $\hier$ transformation between graphs and SCCs. The transformation $a$ represents an interchange of SCCs, $b$ moving a link between nodes in a component and $c$ adding a link. All three transformations represent symmetries of the $\hier$ transformation from graphs to SCCs while only $a$ and $b$ are symmetries of robustness.}
\label{fig:modsccsym}
\end{figure*}

@@

\subsection{Stability and robustness analysis of particular system ensembles}
For systems having two variables, we can analytically compute the probability of stability and robustness from \ref{eq:condprobgen}. For those having three variables, we can estimate these same quantities using Monte Carlo simulations. Systems of larger size can be analyzed using the symmetry properties of robustness extracted from this analysis. For two-variable systems having $2 \times 2$ Jacobian matrices, the aforementioned stability criteria result in the conditions $T < 0$ and $D >
0$ where $T$ and $D$ denote the trace and the determinant. Suppose we have a stable matrix
$$
\begin{bmatrix}
a & b \\
d & c
\end{bmatrix}
$$
where $a + c < 0$ and $ac > bd$.  For the case in which $x_1=a,\,x_2=b,\,x_3=c,\,x_4=d$ we need to compute what corresponds to $R(\mathrm{stab},\mu'_k)$ where $k=1 \ldots 4$. By symmetry, there are two cases to consider; resampling $a$ is equivalent to resampling $c$ and resampling $b$ is equivalent to resampling $d$ so we only need to explicitly compute $ R(\mathrm{stab},\mu'_1)$ and $R(\mathrm{stab},\mu'_2)$. Suppose that we resample $b$ to compute $R(\mathrm{stab},\mu'_2)$.
% \begin{strip}
% \begin{align}\label{eq:condprob}
% P\left(\begin{pmatrix}
% a & b' \\
% d & c
% \end{pmatrix} \textrm{stable } \bigg| \begin{pmatrix}
% a & b \\
% d & c
% \end{pmatrix} \textrm{stable } \right)
% & = \frac{P\left(\begin{pmatrix}
% a & b \\
% d & c
% \end{pmatrix} \textrm{stable and } \begin{pmatrix}
% a & b' \\
% d & c
% \end{pmatrix} \textrm{stable } \right)}{P\left(\begin{pmatrix}
% a & b \\
% d & c
% \end{pmatrix} \textrm{stable } \right)}.
% \end{align}
The denominator of \ref{eq:condprobgen} in this case is given by
\begin{align*}
P\left(\textrm{stab } \left( \begin{bmatrix}
a & b \\
d & c
\end{bmatrix} \right) \right) = \frac{\int_{\genfrac{}{}{0pt}{}{\genfrac{}{}{0pt}{}{ac>bd}{a+c<0}}{H^4}} da\,db\,dc\,dd\,1}{\int_{H^4} da\,db\,dc\,dd\,1}.
\end{align*}
Since the trace does not involve $b$, the $T<0$ condition will be satisfied automatically and we only need to examine the determinant. Thus, we have the inequalities $ac > b'd$ and $-1 < b' < 1$ in addition to the previous constraints leading to an expression for the numerator of \ref{eq:condprobgen}
\begin{widetext}
\begin{align*}
P\left(\textrm{stab} \left( \begin{bmatrix}
a & b \\
d & c
\end{bmatrix} \right) \textrm{ and stab} \left( \begin{bmatrix}
a & b' \\
d & c
\end{bmatrix} \right) \right) = \frac{\int_{{{ac>b'd \atop ac>bd} \atop a+c<0} \atop H^5} da\,db\,dc\,dd\,db'\,1}{\int_{H^5} da\,db\,dc\,dd\,db'\,1}.
\end{align*}
\end{widetext}
The analogous equation for resampling $a$ is
\begin{widetext}
\begin{align*}
P\left(\textrm{stab} \left( \begin{bmatrix}
a & b \\
d & c
\end{bmatrix} \right) \textrm{ and stab} \left( \begin{bmatrix}
a' & b \\
d & c
\end{bmatrix} \right) \right) = \frac{\int_{{{{a'c>bd \atop a' + c < 0} \atop ac>bd} \atop a+c<0} \atop H^5} da\,db\,dc\,dd\,da'\,1}{\int_{H^5} da\,db\,dc\,dd\,da'\,1}.
\end{align*}
\end{widetext}
Using this approach the probability of stability and of robustness for all two variable systems is given in \ref{tab:structstabmat}.

The analogous results for all three variable systems are computed using Monte Carlo integration and shown in \ref{tab:structstabmat3} and \reffigrobustconnect. This process is associated with some error relative to the exact integration described above. If we sample $N = N_{\mathrm{stab}} + N_{\mathrm{unstab}}$ matrices where each has some probability $\theta$ of being stable then $N_{\mathrm{stab}}$ has a binomial distribution. We can compute a sample estimate for $\theta$, $\hat{\theta} = \frac{N_{\mathrm{stab}}}{N}$ \cite{Murphy2012}. The posterior distribution in this case is known to be a Beta distribution as a result of Beta-Binomial conjugacy
$$
\mathrm{Beta}(\theta | \mathcal{D}) = \mathrm{Beta}(\theta | N_{\mathrm{stab}} + a, N_{\mathrm{unstab}} + b)
$$
where $a$ and $b$ are the hyperparameters of the Beta prior and we consider the uninformative uniform prior corresponding to $a=b=1$. We consider the maximum a posteriori estimate
$$\hat{\theta}_{MAP} = \frac{a + N_{\mathrm{stab}} - 1}{a + b + N - 2}$$
which corresponds in this case to the maximum likelihood estimate
$$
\hat{\theta}_{MLE} = \frac{N_{\mathrm{stab}}}{N}.
$$
This estimate is characterized by the variance of the posterior Beta distribution
\begin{widetext}
$$
\mathrm{var}(\theta | \mathcal{D}) = \frac{(a+N_{\mathrm{stab}})(b+N_{\mathrm{unstab}})}{(a + N_{\mathrm{stab}} + b + N_{\mathrm{unstab}})^2(a + N_{\mathrm{stab}} + b + N_{\mathrm{unstab}}+1)}
$$
\end{widetext}
Since for the chosen prior $a=b=1 \ll N$ this simplifies to
$$
\mathrm{var}(\theta | \mathcal{D}) = \frac{\hat{\theta}(1-\hat{\theta})}{N}
$$
yielding the error estimate given by the associated standard deviation. In all simulations we use $N~=~10000$ so that the maximum error for $\hat{\theta}~=~0.5$ is $\sigma~=~\sqrt{\mathrm{var}(\theta | \mathcal{D})} \approx 0.005$.

@@

\begin{figure*}[!ht]
\centering
\noindent\includegraphics[width=0.8\textwidth]{fig/combinedfigs.pdf}
\caption{{\bf Characterization of stability and robustness according to properties of system structure for three variable systems} (A) Robustness versus connectivity. The red line represents a best fit in the least-squares sense with Pearson product-moment correlation coefficient $r=0.29$. The lowest and highest robustness network architectures are labelled. Other network architectures are shown in \ref{tab:structstabmat3}. (B) Robustness versus hierarchy. Correlation coefficient $r=0.67$. (C) Number of cycles and (D) hierarchy vs connectivity and robustness. The color of each point represents the average robustness of all graphs having the parameters specified on the $x$ and $y$ axes.
}
\label{fig:combined}
\end{figure*}

@@

Using these observations, we may express the robustness of a graph in
terms of the robustnesses of its strongly connected components.  If
each component $C_i$ of our graph $G$ has $v_i$ vertices, connectivity
$\connectivity_i$, and there are $\ell_{ij}$ links between components
$i$ and $j$, then there are a total of
$\sum_{i,j \in \hier(G)} \ell_{ij} + \sum_{i=1}^n \connectivity_i$
links in $G$.  If we resample a randomly chosen link in a component
$C_i$, then the probability that the system will remain stable after
resampling is $\langle R(\hbox{stab} (C_i), \mu') \rangle_1$.  If we resample a link
between components $C_i$ and $C_j$, the system will remain stable with
probability 1.  Hence, the probability that the system will remain
stable upon resampling a random link is the weighted average of these
probabilities:
\begin{widetext}
\begin{align}\label{eq:sccrobustness}
\langle R(\hbox{stab} (G), \mu') \rangle_1 =
\frac{\sum\limits_{(i,j) \in \hier(G)} \ell_{ij} +
      \sum\limits_{i=1}^n \connectivity_i \langle R(\textrm{stab}(C_i),\mu') \rangle_1}
     {\sum\limits_{(i,j) \in \hier(G)} \ell_{ij} +
      \sum\limits_{i=1}^n \connectivity_i}.
\end{align}
\end{widetext}
For instance, if our graph is the one in \reffigscc (middle panels), then we have two connected components, one with two nodes, and one with one node.  From \ref{tab:structstabmat}, we know that the graph with two nodes has probability $0.25$ of being stable and robustness $0.62$.  The graph with one node corresponds to a $1 \times 1$ matrix, so we have probability $0.5$ of stability and robustness $0.5$.  Thus, the probability of our 3-node graph being stable is $0.5 \times 0.25 = 0.125$ and its robustness is
\[
\langle R(\textrm{stab}(G),\mu') \rangle_1 = \frac{2 + 0.5 + 4 \times 0.62}{2 + 1 + 4} = 0.714,
\]
which agrees with the value computed in \ref{tab:structstabmat} up to
sampling error.

@@

Since every acyclic digraph can be embedded into a totally ordered
set, we may assume without loss of generality that our components have
been ordered in a way such that, if $(i,j) \in \hier(G)$, then $i <
j$.  Hence, after substituting into our expression and simplifying
using the identity
$$\sum_{i=1}^{n-1}\sum_{j=i+1}^{n}v_i
v_j~=~\frac{1}{2} \left( \sum_{i=1}^{n} v_i \right)^2-\frac{1}{2} \sum_{i=1}^{n}
v_i^2,$$
we arrive at the following upper bound on robustness in terms
of the connected components:
\begin{widetext}
\begin{align} \label{eq:sccmaxrobustness}
R_{\mathrm{max}}(C_1, \ldots C_n) =
\frac{\frac{1}{2} ((\sum_{i=1}^n v_i)^2 - \sum_{i=1}^n v_i^2) +
                    \sum_{i=1}^n \connectivity_i \langle R(\hbox{stab}(C_i),\mu') \rangle_1}
     {\frac{1}{2} ((\sum_{i=1}^n v_i)^2 - \sum_{i=1}^n v_i^2) +
                    \sum_{i=1}^n \connectivity_i}.
\end{align}
\end{widetext}
Furthermore, this bound is attained.  Suppose that $G_{\mathrm{tot}}$
is the graph on $n$ nodes with a link from node $i$ to node $j$
whenever $i < j$.  Then, by the construction described in the previous
section on network hierachy, we have a graph $G_{\mathrm{max}}$ such
that the components of $G_{\mathrm{max}}$ are $C_1, \ldots C_n$ and
$\hier (G_{\mathrm{max}}) = G_{\mathrm{tot}}$.  By our formula,
$\langle R(\hbox{stab} (G_{\mathrm{max}}), \mu') \rangle_1 = R_{\mathrm{max}}(C_1, \ldots C_n)$.

This argument also works when we resample more than one entry,
although the notation becomes more complicated.  Suppose that we
resample $m$ nodes.  Define
\begin{widetext}
\begin{equation*}
M = \left\{(m_0, m_1, \ldots, m_n) \,\bigg|\,
m = \sum_{i=0}^n m_i \quad\&\quad
m_0 \le \sum_{i=1}^{n-1} \sum_{j=i+1}^n \ell_{ij} \quad\&\quad
(\forall i \in \{1, \ldots, n\}) \; m_i < \connectivity_i \right\}.
\end{equation*}
\end{widetext}
Then, given $(m_0, m_1, \ldots, m_n) \in M$, there are ${m \choose
m_0, m_1, \ldots. m_n}$ ways of choosing $m_i$ links from $C_i$ and
$m_0$ links between strongly connected components.  Hence, our
weighted average becomes
\begin{widetext}
\begin{equation}
\langle R(\hbox{stab} (G), \mu') \rangle_m =
\frac{\sum\limits_{(m_0, m_1, \ldots m_n) \in M}
      {m \choose m_0, m_1, \ldots. m_n}
      \left(m_0 + \sum\limits_{i=1}^n m_i \langle R(\hbox{stab} (C_i), \mu') \rangle_{m_i} \right)}
     {\sum\limits_{(m_0, m_1, \ldots m_n) \in M}
      {m \choose m_0, m_1, \ldots. m_n} m}
\end{equation}
\end{widetext}
